Stack Safety as Security Property

### 2020-05-27 main.tex
Paper on formal CHERI security properties
Outline

\title{Interfering with Noninterference
\iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF
    and...?)}}\fi
}

@@

@@

@@

>>>>

\title{Stack Safety as Security Property}
%\title{The Meaning of/What is Stack Safety}
\iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF
    and...?)}}\fi
}

@@

\section{Introduction}

Everybody likes stack safety. Nobody can say what it is precisely.

The intention is to protect callers from callees.

Examples of what it isn't in the literature.
Small bad examples of things that can go wrong.

Turn this into a positive security property: integrity + confidentiality.

Challenges?
Shifting notion of who the attacker is throughout execution.

Roadmap: 
Preliminaries before all these.

Contributions:
\begin{itemize}
\item A formal property capturing the informal understanding of what ``stack safety'' is.
\item Evidence that this property really does capture the folk intuition: we show that the stack
  unsafe examples from the literature also fail our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism.
\item A (inductive? step-by-step/stepwise) variant of this property
  tuned for testing/verification together with a proof that it implies
  the original property.  We test the whole thing with a cool
  framework.
\item A lazy version of the property that allows for more efficient/dynamic enforcement.
  Maybe testing.
\item TODO: Logic? Reasoning Principles?
\end{itemize}

Related work pointer + conclusions.

\section{Preliminaries/Background}
%\input{props}

\begin{itemize}
\item machine model
\item Calling conventions
\end{itemize}

\section{Related Work}

@@

\section{Future Work}

Is there a knowledge-based presentation of all this?

@@

\item Rigorous engineering for hardware security: Formal modelling and proof in
the CHERI design and implementation process
\url{https://www.cl.cam.ac.uk/research/security/ctsrd/pdfs/202005oakland-cheri-formal.pdf}
